Waking up a sleeping rabbit:\\ On Natural-Language Sentence Generation with FF

### 2010-03-01 trunk/Papers/crisp-ff-10/experiments.tex
Joerg final

Results for $d=2$ are shown in Fig.~\ref{fig:runtimes} (b).  Here the
old FF preprocessor crashed with a segmentation fault even at
$n=1$. LAMA performs better, but times out beyond $n>2$.  Best-first
search with helpful actions is clearly the best-performing search
strategy here.  It takes about 14 seconds for $n=3$, but this sentence
is already quite long at 29 words, and EHC takes 3.5 minutes on the
same input.  Best-first search without helpful actions timed out at
$n=3$, illustrating the importance of that heuristic.

The relative behavior of the different search methods is not uniform
in our domain, which exhibits a huge amount of structural variance due
to the many different forms that the input grammar may take. We are
far from an exhaustive exploration of all the possible parameter
settings. For instance, with particular inputs (no distractors), EHC
can be more effective than best-first search.

>>>>

Results for $d=2$ are shown in Fig.~\ref{fig:runtimes} (b).  Here the
old FF preprocessor crashed with a segmentation fault even at
$n=1$. LAMA performs better, but times out beyond $n>2$.  Best-first
search with helpful actions is clearly the best-performing search
strategy here.  It takes about 14 seconds for $n=3$, but this sentence
is already quite long at 29 words, and EHC takes 3.5 minutes on the
same input.  Best-first search without helpful actions timed out at
$n=3$, illustrating the importance of that pruning technique.

We remark that the relative behavior of the different search methods
is not uniform in our domain, which exhibits a huge amount of
structural variance due to the many different forms that the input
grammar may take. We are far from an exhaustive exploration of all the
possible parameter settings. For instance, with particular inputs (no
distractors), EHC can be more effective than best-first search.
